Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-12-21 ms.tex
units for BDs

\subsection{Photometric Monitoring}
We monitored WASP-103's photometric variability over 158 nights during 2014 - 2016 with the Tennessee State University Celestron 14-inch (C14) automated imaging telescope (AIT), located at Fairborn Observatory in southern Arizona \citep[see, e.g.,][]{h1999, ehf2003}.  The observations of WASP-103 were made in the Cousins R passband with an SBIG STL-1001E CCD camera.  Each observation consisted of 4--10 consecutive exposures on WASP-103 along with several dozen comparison stars in the same field. The individual consecutive frames were co-added and reduced to differential magnitudes (i.e., WASP-103 minus the mean brightness of the six best comparison stars). The nightly observations were corrected for bias, flat-fielding, pier-side offset, and differential atmospheric extinction.

@@

\begin{deluxetable}{ccccc}
	%\tabletypesize{\small}
	\tablenum{1}
	\tablewidth{0pt}
	\tablecaption{Photometric Observations of WASP-103}
	\tablehead{
		\colhead{Observing} & \colhead{} & \colhead{Date Range} &
	\colhead{Sigma} & \colhead{Seasonal Mean} }% \\

@@

	%	\colhead{(1)} & \colhead{(2)} & \colhead{(3)} &
	%	\colhead{(4)} & \colhead{(5)}  
	\startdata
	   2014   &  59 & 56722--56972 & 0.0057 & $0.9546\pm0.0007$  \\
	   2015   &  73 & 57028--57335 & 0.0062 & $0.9549\pm0.0007$  \\
	   2016   &  26 & 57385--57451 & 0.0055 & $0.9485\pm0.0011$  \\
	\enddata
	\label{tab:photometry}
\end{deluxetable}

@@

We calculated the planet-to-star flux $F_p/F_s$ in two different ways. First, we fit a sinusoid with a period equal to the planet's orbital period. The free parameters were the sine curve amplitude and phase offset. For the second approach, we used the \texttt{SPIDERMAN} package \citep{louden17} to model $F_p/F_s$. This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$. In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}.  For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).  In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis.

We scaled the planet-to-star flux by a correction factor $c$ to account for dilution from the companion star and ellipsoidal variability due to the planet's tidal distortion. The correction factor took the form: 
\begin{equation}
	c(\lambda, t) = [1 + \alpha(\lambda)]A(t)
\end{equation}
where $\alpha(\lambda)$ is the additional fractional flux from the companion star and $A(t)$ is the sky-projected area of the planet. We estimated $\alpha(\lambda)$ based on the best fit spectral energy distribution from \cite{cartier17}. The companion star contributes FIXME percent of the flux at FIXME $\mu$m.  We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid. We estimated the ellipsoid properties using Table B.3 of \cite{leconte11a}, assuming the planet radius is 1.5 $R_\mathrm{Jup}$ and age is 5 Gyr. The predicted ellipsoidal variability is shown in Figure\,\ref{fig:ellipsoidal}. At quadrature, the projected radius is $8\%$ larger than at phase zero (mid-transit). %FIXME: say this doesn't matter.
%In addition to temperature, the planet's visible surface area $[R(t)]^2$ is also expected to vary with orbital phase due to tidal distortion \citep{gillon14}. In the observed light curve, changes in planet radius are degenerate with changes in temperature.

@@

\subsection{Systematics}
Both the \HST\ and \Spitzer\ phase curves have systematic noise caused by variations in the sensitivity of the instrument over time. For the \HST/WFC3 data, the dominant systematic is an orbit-long exponential trend due to charge traps filling up over successive exposures \citep{long15, zhu17}. For \Spitzer\, the primary source of noise is the intrapixel sensitivity effect. The detector's pixels do not have uniform sensitivity, so slight changes in telescope pointing cause the recorded flux to vary. In Figure\,\ref{fig:systematics}, we show the raw light curves before systematic noise was removed. The systematics have comparable amplitude to the thermal phase variation signal, so they must be carefully corrected to recover the underlying planet-to-star flux.

@@

As discussed in \S \ref{label:fitquality}, the 3.6 $\mu$m light curve exhibits time correlated noise. To account for this additional source of error, we fit the wavelet model from \cite{carter09} (simultaneously with the other fit parameters). FIXME: describe wavelets.

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/phase_curves.pdf}
\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom). For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1. The left column shows the phase curves with systematic noise removed (black points) compared to the best fit model (black line). The shading denotes the  1\,$\sigma$ confidence interval on the best fit. We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve.}
\label{fig:phasecurves}
\end{figure*}

@@

\subsection{Goodness of Fit}
We performed several tests of the quality of the light curve fits.  First we predicted the level of scatter in the light curves based on photon noise alone, then compared this value to the root-mean-square (rms) of the fit residuals.  The Spitzer 4.5 $\mu$m light curve rms is within 10\% of the expected photon noise limit (691 versus 640 ppm), whereas the 3.6 $\mu$m light curve has significantly larger rms (797 versus 470 ppm), due to time-correlated red noise (discussed below). The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 parts per million (ppm), and the measured rms was typically within 5\% of expectations for all spectroscopic channels.  For the WFC3 band- integrated white light curve, the rms was slightly larger than predicted (175 versus 122 ppm). There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, loss of flux outside the extraction window, and imperfect modeling of the astrophysical signal or instrument systematics. However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (which reach the photon limit), so we do not further explore the small excess noise in the white light curve.

@@

\begin{deluxetable}{llllll}
	\tablecolumns{6}
	\tablewidth{0pt}:
	\tablecaption{Model Comparison \label{table:models}}
	\tablehead{
	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
		\startdata
		WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
		\, & Sinusoid & -- & -- & 17.7 & 13.2 \\
		Ch 1 & Sph. Harmonics & 1280 & 3444 & 48.0 & 0.0 \\
		\, & Kinematic & 1955 & 3675 & 82.3 & 34.3 \\
		\, & Two Temp. & 1429 & 3041 & 58.7 & 17.6 \\
		\, & Sinusoid & -- & -- & 0.0 & 98.4 \\
		Ch 2 & Sph. Harmonics & 902 & 3786 & 2.2 & 3.1 \\
		\, & Kinematic & 1703 & 4276 & 16.55 & 17.41 \\
		\, & Two Temp. & 1361 & 3311 & 26.1 & 0.0 \\
		\, & Sinusoid & -- & -- & 0.0 & 49.6 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
\end{deluxetable}

\subsection{Phase-Resolved Spectra}
We used the best-fit phase curves (with systematics removed) to generate phase-resolved emission spectra.  Since our model does not fit eclipse depth as a free parameter, we estimated the dayside emission spectrum as follows. We used \texttt{SPIDERMAN}'s eclipse\_depth method to calculate the average planet-to-star flux for the best-fit model during secondary eclipse.  To estimate uncertainties, we took the standard deviation of the residuals of the in-eclipse data points, then added this value in quadrature to the standard deviation of the residuals of the out-of-eclipse data.  This quadrature sum accounts for the uncertainty in the baseline flux.

For the other orbital phases, we binned the light curve (with systematics removed) in eight intervals of about 0.1 in orbital phase, with endpoints at phases $0.06, 0.15, 0.25, 0.35, 0.44$ and $0.56, 0.65, 0.75, 0.85, 0.94$. These endpoints were chosen to ensure that there is no contribution from in-transit or in-eclipse data.  In each phase bin, we estimated the planet-to-star flux from the mean value of the data points in the bin. To estimate the uncertainty, we took the standard deviation of the points in the bin and added it in quadrature to the standard deviation of the data points during secondary eclipse (phase $0.46-0.54$), to account for the uncertainty in baseline stellar flux. The phase-resolved emission spectra are shown in Figure\,\ref{fig:spectra} and listed in Table\,\ref{table:spectra}.

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
\caption{Phase-resolved emission spectra.}
\label{fig:spectra}
\end{figure*}

@@

\subsection{Comparison of Thermal Phase Variation Models}
We compared four different models for the thermal phase variation: a sinusoid and three temperature maps. The sinusoid has been the most widely used model for thermal phase variation in previous analyses of thermal phase curves \citep{FIXME} and directly fits the phase variation amplitude and offset from the substellar point. Fitting temperature maps (two-temperature, kinematic, and spherical harmonics) is a new approach enabled by the \texttt{SPIDERMAN} package.  The three maps each have different strengths: the kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.   The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate. The two-temperature model is the simplest and easiest to compare to one-dimensional models of the dayside, which assume a uniform temperature/pressure profile.

@@

%\section{Analysis}
%In this section we describe the interpretation of the data using simple blackbody models, a 1-D grid-based retrieval, and 3-D general circulation models (GCMs).

@@

\subsection{Clouds?}

@@

We also fit blackbody models to the WFC3 data only, and found that they provide a good fit at all orbital phases. The $\chi^2_\nu$ values range from 0.5 to 1.6, with a median of 0.9. The best fit effective temperatures range from 1920 Kelvin on the nightside to 2980 Kelvin on the dayside. We report the best fit temperatures with uncertainties in Table\,\ref{tab:depths}.  The dayside spectrum is the poorest fit by the blackbody model. This finding is not a surprise because the dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \citep{cartier17}. The more sophisticated grid-based retrieval provides a better fit to the dayside.

@@

At each point in the grid, we compute forward models to determine self-consistent, radiative-convective temperature-pressure (T-P) profiles. We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium.  We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, and VO (\textbf{Mike: what others?}). Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates at dayisde photospheric temperature and pressure (3000 K, 0.1 bar).  Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13}, and interpolated in the grid to calculate the likelihood at each model step. We retrieved the composition for dayside emission spectrum and at FIXME phases

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs_02.pdf}
\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum. The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% confidence interval. The colored shading on the off-diagonal panels indicates FIXME. The blue lines correspond to solar metallicity (1) and C/O (0.54).}
\label{fig:composition}
\end{figure}

\subsubsection{Dayside Spectrum}
The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.  The best fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77. The WFC3 and Spitzer $3.6\,\mu$m points are fit better ($\chi^2_\nu$  = 1.17 for these data alone), but the $4.5\,\mu$m point is in tension with the model at FIXME $\sigma$.  The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).

@@

The TiO/VO absorption heats the upper atmosphere, resulting in a thermal inversion. Figure\,\ref{fig:TP} shows a selection of 100 randomly selected dayside T-P profiles. The profiles are nearly isothermal over a pressure range of $1-10^{-2}$ bars, with a median temperature near 2900 Kelvin. The temperature increases over $10^{-2} - 10^{-3}$ bars to 3500 Kelvin, and then begins to decrease again at pressures below $10^{-3}$ bar. FIXME: where are the contribution functions for the different instruments?

@@

\subsubsection{Nightside Spectrum}
We also fit the nightside spectrum (phase $0.1$) with the grid-based retrieval. The best fit spectrum has a non-inverted temperature pressure profile.  At 1\,$\sigma$ confidence, the metallicity is $15 - 240\times$ solar and the C/O is unbounded over the full prior range (FIXME). The atmospheric composition is consistent with results from the dayside spectrum.

This agreement is an encouraging sanity check; however, there are several model assumptions that may result in artificially tight constraints on the atmospheric properties.  One challenge in modeling the nightside spectrum is that the shape of the T-P profile is unknown.  Our model assumes a scaled stellar irradiation at the top of the atmosphere, but in reality, the heat source is advection from the dayside. Another caveat is that the model is not self-consistent: the energy leaving the dayside is not constrained to equal the energy entering the nightside.  We do not pursue this, but note these for future phase curve observations that are sensitive to spectral Future work is needed to develop a self-consistent 2-D retrieval method to fit phase curve.

@@

\subsection{Comparison with GCMs}
To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. We used the SPARC

>>>>

\subsection{Photometric Monitoring}
We monitored WASP-103's photometric variability over 158 nights during 2014 - 2016 with the Tennessee State University Celestron 14-inch (C14) automated imaging telescope (AIT), located at Fairborn Observatory in southern Arizona \citep[][]{henry99}.  The observations of WASP-103 were made in the Cousins R passband with an SBIG STL-1001E CCD camera.  Each observation consisted of 4--10 consecutive exposures on WASP-103 along with several dozen comparison stars in the same field. The individual consecutive frames were co-added and reduced to differential magnitudes (i.e., WASP-103 minus the mean brightness of the six best comparison stars). The nightly observations were corrected for bias, flat-fielding, pier-side offset, and differential atmospheric extinction.

@@

\begin{deluxetable}{ccccc}
\label{tab:photometry}
	%\tabletypesize{\small}
	\tablenum{1}
	\tablewidth{0pt}
	\tablecaption{Photometric Observations of WASP-103}
	\tablehead{
		\colhead{Observing} & \colhead{} & \colhead{Date Range} &
	\colhead{Sigma} & \colhead{Seasonal Mean} }% \\

@@

	%	\colhead{(1)} & \colhead{(2)} & \colhead{(3)} &
	%	\colhead{(4)} & \colhead{(5)}  
	\startdata
	   2014   &  59 & 56722--56972 & 0.0057 & $0.9546\pm0.0007$  \\
	   2015   &  73 & 57028--57335 & 0.0062 & $0.9549\pm0.0007$  \\
	   2016   &  26 & 57385--57451 & 0.0055 & $0.9485\pm0.0011$  \\
	\enddata
\end{deluxetable}

@@

We calculated the planet-to-star flux $F_p/F_s$ in two different ways. First, we fit a sinusoid with a period equal to the planet's orbital period. The free parameters were the sine curve amplitude and phase offset. For the second approach, we used the \texttt{SPIDERMAN} package \citep{louden17} to model $F_p/F_s$. This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$. In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}.  For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang17}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).  In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis.

We scaled the planet-to-star flux by a correction factor $c$ to account for dilution from the companion star and ellipsoidal variability due to the planet's tidal distortion. The correction factor took the form: 
\begin{equation}
	c(\lambda, t) = [1 + \alpha(\lambda)]A(t)
\end{equation}
where $\alpha(\lambda)$ is the additional fractional flux from the companion star and $A(t)$ is the sky-projected area of the planet. We estimated $\alpha(\lambda)$ based on the best fit spectral energy distribution from \cite{cartier17}. The companion star contributes $10-16\%$ of the flux over the wavelength range $1 - 5\,\mu$m.  We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid. We estimated the ellipsoid properties using Table B.3 of \cite{leconte11a}, assuming the planet radius is 1.5 $R_\mathrm{Jup}$ and age is 5 Gyr. The predicted ellipsoidal variability is shown in Figure\,\ref{fig:ellipsoidal}. At quadrature, the projected radius is $8\%$ larger than at phase zero (mid-transit). %FIXME: say this doesn't matter.
%In addition to temperature, the planet's visible surface area $[R(t)]^2$ is also expected to vary with orbital phase due to tidal distortion \citep{gillon14}. In the observed light curve, changes in planet radius are degenerate with changes in temperature.

@@

\subsection{Systematics}
Both the \HST\ and \Spitzer\ phase curves have systematic noise caused by variations in the sensitivity of the instrument over time. For the \HST/WFC3 data, the dominant systematic is an orbit-long exponential trend due to charge traps filling up over successive exposures \citep{long15, zhou17}. For \Spitzer\, the primary source of noise is the intrapixel sensitivity effect. The detector's pixels do not have uniform sensitivity, so slight changes in telescope pointing cause the recorded flux to vary. In Figure\,\ref{fig:systematics}, we show the raw light curves before systematic noise was removed. The systematics have comparable amplitude to the thermal phase variation signal, so they must be carefully corrected to recover the underlying planet-to-star flux.

@@

As discussed in \S \ref{sec:fitquality}, the 3.6 $\mu$m light curve exhibits time correlated noise. To account for this additional source of error, we fit the wavelet model from \cite{carter09} (simultaneously with the other fit parameters). FIXME: describe wavelets.

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/phase_curves_spherical.pdf}
\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom). For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1. The left column shows the phase curves with systematic noise removed (black points) compared to the best fit spherical harmonics model (colored lines). The error bars denote $1\,\sigma$ uncertainties (in some cases, the errors are smaller than the data points).
%The shading denotes the  1\,$\sigma$ confidence interval on the best fit. 
We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve.}
\label{fig:phasecurves}
\end{figure*}

@@

\subsection{Goodness of Fit}
\label{sec:fitquality}
We performed several tests of the quality of the light curve fits.  First we predicted the level of scatter in the light curves based on photon noise alone, then compared this value to the root-mean-square (rms) of the fit residuals.  The Spitzer 4.5 $\mu$m light curve rms is within 10\% of the expected photon noise limit (691 versus 640 ppm), whereas the 3.6 $\mu$m light curve has significantly larger rms (797 versus 470 ppm), due to time-correlated red noise (discussed below). The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 parts per million (ppm), and the measured rms was typically within 5\% of expectations for all spectroscopic channels.  For the WFC3 band- integrated white light curve, the rms was slightly larger than predicted (175 versus 122 ppm). There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, loss of flux outside the extraction window, and imperfect modeling of the astrophysical signal or instrument systematics. However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (which reach the photon limit), so we do not further explore the small excess noise in the white light curve.

@@

\begin{deluxetable}{llllll}
\label{tab:model_comparison}
	\tablecolumns{6}
	\tablewidth{0pt}:
	\tablecaption{Model Comparison \label{table:models}}
	\tablehead{
	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
		\startdata
		WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
		\, & Sinusoid & -- & -- & 17.7 & 13.2 \\
		Ch 1 & Sph. Harmonics & 1280 & 3444 & 48.0 & 0.0 \\
		\, & Kinematic & 1955 & 3675 & 82.3 & 34.3 \\
		\, & Two Temp. & 1429 & 3041 & 58.7 & 17.6 \\
		\, & Sinusoid & -- & -- & 0.0 & 98.4 \\
		Ch 2 & Sph. Harmonics & 902 & 3786 & 2.2 & 3.1 \\
		\, & Kinematic & 1703 & 4276 & 16.55 & 17.41 \\
		\, & Two Temp. & 1361 & 3311 & 26.1 & 0.0 \\
		\, & Sinusoid & -- & -- & 0.0 & 49.6 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
\end{deluxetable}

\subsection{Phase-Resolved Spectra}
We used the best-fit phase curves (with systematics removed) to generate phase-resolved emission spectra.  Since our model does not fit eclipse depth as a free parameter, we estimated the dayside emission spectrum as follows. We used \texttt{SPIDERMAN}'s eclipse\_depth method to calculate the average planet-to-star flux for the best-fit model during secondary eclipse.  To estimate uncertainties, we took the standard deviation of the residuals of the in-eclipse data points, then added this value in quadrature to the standard deviation of the residuals of the out-of-eclipse data.  This quadrature sum accounts for the uncertainty in the baseline flux. To account for red noise in the \Spitzer\ $3.6\,\mu$ light curve, we use the approach of \cite{pont06} to determine the red noise contribution on the timescale of the eclipse. We add the estimated red noise in quadrature, which increases the uncertainty on planet-to-star flux by a factor of $2.5$.

For the other orbital phases, we binned the light curve (with systematics removed) in eight intervals of about 0.1 in orbital phase, with endpoints at phases $0.06, 0.15, 0.25, 0.35, 0.44$ and $0.56, 0.65, 0.75, 0.85, 0.94$. These endpoints were chosen to ensure that there is no contribution from in-transit or in-eclipse data.  In each phase bin, we estimated the planet-to-star flux from the mean value of the data points in the bin. To estimate the uncertainty, we took the standard deviation of the points in the bin and added it in quadrature to the standard deviation of the data points during secondary eclipse (phase $0.46-0.54$), to account for the uncertainty in baseline stellar flux.  For the $3.6\mu$m data, we also add red noise on the timescale of a phase bin, following \cite{pont06}.  The phase-resolved emission spectra are shown in Figure\,\ref{fig:spectra} and listed in Table\,\ref{table:spectra}.

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the FIXME GCM. Phases $\phi = 0.5$ and $0.0$ are centered on the substellar and anti-stellar points, respectively.}
\label{fig:spectra}
\end{figure*}

@@

\subsection{Comparison of Thermal Phase Variation Models}
We compared four different models for the thermal phase variation: a sinusoid and three temperature maps. The sinusoid has been widely used to model phase variation in previous analyses \citep[e.g.][]{knutson09, stevenson14}. One advantage of the sinusoid model is that it directly fits the phase variation amplitude and offset from the substellar point, and can be inverted to map the climate \citep{cowan08}. Fitting temperature maps directly is a new approach enabled by the \texttt{SPIDERMAN} package.  We consider three parameterizations for the temperature map, which each have different strengths. One is a physically-motivated kinematic model that closely reproduces GCM simulations \citep{zhang17}.  The second parameterization is a spherical harmonic map, which is the most flexible model we consider and makes the fewest assumptions about the true climate. The third model has just two free parameters, a dayside temperature and a nightside temperature. This model is easiest to compare to one-dimensional forward models of the dayside, which assume a uniform temperature/pressure profile.

@@

@@

%\subsection{Clouds?}

@@

We also fit blackbody models to the WFC3 data only, and found that they provide a good fit at all orbital phases. The $\chi^2_\nu$ values range from 0.5 to 1.6, with a median of 0.9. The best fit effective temperatures range from 1920 Kelvin on the nightside to 2980 Kelvin on the dayside. We report the best fit temperatures with uncertainties in Table\,\ref{tab:depths}.  The dayside spectrum is the poorest fit by the blackbody model. This finding is not a surprise because the dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}. The more sophisticated grid-based retrieval provides a better fit to the dayside.

@@

At each point in the grid, we compute forward models to determine self-consistent, radiative-convective temperature-pressure (T-P) profiles. We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium.  We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, and VO (\textbf{Mike: what others?}). Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates at dayisde photospheric temperature and pressure (3000 K, 0.1 bar).  Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13}, and interpolated in the grid to calculate the likelihood at each model step. We fit this model to the dayside and nightside emission spectra (phases $\phi = 0.5$ and $0.1$).

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs_02.pdf}
\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum. The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% confidence interval. \textbf{Mike: what percentiles does the colored shading correspond to?} The blue lines correspond to solar metallicity (1) and C/O (0.54).}
\label{fig:composition}
\end{figure}

\subsubsection{Dayside Spectrum}
The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.  The best fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77. The WFC3 and Spitzer $3.6\,\mu$m points are fit better ($\chi^2_\nu$  = 1.17 for these data alone), but the $4.5\,\mu$m point is higher than the best fit model by $2.9\,\sigma$.  The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).

@@

The TiO/VO absorption heats the upper atmosphere, resulting in a thermal inversion. Figure\,\ref{fig:TP} shows a selection of 100 randomly selected dayside T-P profiles. The profiles are nearly isothermal over a pressure range of $1-10^{-2}$ bars, with a median temperature near 2900 Kelvin. The temperature increases over $10^{-2} - 10^{-3}$ bars to 3500 Kelvin, and then begins to decrease again at pressures below $10^{-3}$ bar. (\textbf{Mike: what are the contribution functions?}).

@@

\subsubsection{Nightside Spectrum}
We also fit the nightside spectrum (phase $0.1$) with the grid-based retrieval. The best fit spectrum has a non-inverted temperature pressure profile.  At 1\,$\sigma$ confidence, the metallicity is $15 - 240\times$ solar and the C/O is unbounded over the full prior range (\textbf{Mike: what priors did you use?}). The atmospheric composition is consistent with results from the dayside spectrum.

This agreement is an encouraging sanity check; however, there are several model assumptions that may result in artificially tight constraints on the atmospheric properties.  One challenge in modeling the nightside spectrum is that the shape of the T-P profile is unknown.  Our model assumes a scaled stellar irradiation at the top of the atmosphere, but in reality, the heat source is advection from the dayside. Another caveat is that the model is not self-consistent: the energy leaving the dayside is not constrained to equal the energy entering the nightside.  Further work is needed to develop a fully self-consistent 2-D retrieval method.

@@

\subsection{Comparison with GCMs}
To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra.
